Proyecto: Crecimiento economice y su relación con energías limpias en la región latinoamericana

### 2020-05-04 Propuesta/main.tex
Updates from Overleaf
Add risk matrix
Add risk matrix 
Add title to the document

\input{structure.tex} % Include the file specifying the document structure and custom commands

@@

\title{Proyecto: Nombre Proyecto} % Title of the assignment

@@

>>>>

\input{structure.tex} % Include the file specifying the document structure and custom commands
\usepackage[table]{xcolor}

@@

\title{Proyecto: Crecimiento economice y su relación con energías limpias en la región latinoamericana} % Title of the assignment

@@

%The below command generates a 4 X 5 risk matrix with ALARP regions for initial risk matrix.

\begin{table}[H]
\centering
\scriptsize
\caption{Initial risk matrix}
\begin{tabular}{|p{2cm}|p{2cm}|p{2cm}| p{2cm} |p{2cm}| p{2cm}|}
\hline \bf Frecuencia/Consecuencia & \bf Poco Probable & \bf Probable & \bf Ocasionalmente & \bf Probable & \bf Bastante Probable\\ [10pt]

\hline \bf 4-Catastrófico & \cellcolor{yellow!50} & \cellcolor{red!50} & \cellcolor{red!50} & \cellcolor{red!50} &\cellcolor{red!50} \\ [10pt]

\hline \bf 3-Critico &\cellcolor{green!50} & \cellcolor{yellow!50} & \cellcolor{yellow!50} & \cellcolor{red!50} &\cellcolor{red!50} \\ [10pt]

\hline \bf 2-Mayor & \cellcolor{green!50} & \cellcolor{green!50} & \cellcolor{yellow!50} &\cellcolor{yellow!50} &\cellcolor{red!50} \\ [10pt]

\hline \bf 1-Menor & \cellcolor{green!50} & \cellcolor{green!50} & \cellcolor{green!50} &\cellcolor{yellow!50} &\cellcolor{yellow!50} \\ [10pt]
\hline
\end{tabular} \\
\end{table}

%The command below provides the legend for the Risk Matrix

\begin{table}[H]
\centering
%\scriptsize
\caption{Legenda de color de la matriz de riesgo}
\begin{tabular}{|p{2cm}|p{10cm}|}
\hline \bf Color & \bf Legenda \\
\hline \cellcolor{red! 50} & Aceptable - Se requiere reducción de riesgo\\ [10pt]
\hline \cellcolor{yellow! 50} & Aceptable - Considere reducir el riesgo. \\[10pt]
\hline \cellcolor{green! 50} & Aceptable \\ [10pt]
\hline
\end{tabular}
\end{table}
